---
title: "Assignment 12"
author: "Hannah Kosinovsky"
date: "11/27/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Question 1: Warm Up: Brief Financial Data 

##a) EuStockMarkets
```{r,echo = TRUE}
help(EuStockMarkets) 
EuStockMarkets
```

##b) simple plot
```{r,echo = TRUE}
DAX = EuStockMarkets[,1]
plot(DAX, xlab = "Year", ylab = "Daily Closing Prices DAX", main = "Daily Dax Closer prices 1991-1998", col = "blue")
abline(v=1997, col="red")
```

##c) decompose
```{r,echo = TRUE}
#install.packages("forecast")
library(forecast)
decomp.dax = decompose(DAX) 
plot(decomp.dax, xlab = "Year", ylab = "Daily Closing Prices DAX", col = "blue")
abline(v=1997, col="red")
```

#Question 2: Temperature Data

##a) Examine data
```{r,echo = TRUE}
#install.packages('fpp2', dependencies = TRUE)
library(fpp2)
help(maxtemp)
maxtemp<- ts(maxtemp, frequency=12, start=c(1971,1))

autoplot(maxtemp)
```

##b) Subset of data after 1990
```{r,echo = TRUE}
#info after 1990
maxtemp.90s<-window(maxtemp, start=1990)
autoplot(maxtemp.90s)
```


##c)	Utilize SES to predict the next five years of maximum temperatures in Melbourne
```{r,echo = TRUE}
ses(maxtemp.90s, h = 5, level = 95)
plot(maxtemp.90s)
fit <- ses(maxtemp.90s, h = 5, level = 95)
#attributes(fit)
plot(fit, ylab="Temperature", xlab="Year", main="Forecast of Max Temperatures")
fit$model
```

##d)	Utilize damped Holt's linear trend to predict the next five years of maximum temperatures in Melbourne
```{r,echo = TRUE}
holtfit <- holt(maxtemp.90s, initial="optimal", h=5, damped=TRUE)
plot(holtfit, ylab="Temperature", xlab= "Year", main="Forecast")
lines(fitted(holtfit), col="blue", type="o")
holtfit$model
```


##e)	Compare the AICc 

###The model with lower AIC is the better model. The AIC from the damped Holt method is 141.38.
###The AIC from the SES model is 140.48. Therefore, the SES model is better

#Question 3: The Wands Choose the Wizard 

##a) Read in data
```{r,echo = TRUE}
Gregorovitch = read.csv(file="~/Downloads/MSDSUNIT12Assignment/Unit11TimeSeries_Gregorovitch.csv", header = FALSE)
Olivander = read.csv(file="~/Downloads/MSDSUNIT12Assignment/Unit11TimeSeries_Ollivander.csv", header = FALSE)
```

##b) Convert the data
```{r,echo = TRUE}
#convert first column to date class object
Gregorovitch$V1 = as.Date(Gregorovitch$V1, format = "%m/%d/%Y")
Olivander$V1 = as.Date(Olivander$V1, format = "%m/%d/%Y")
```

##c) Convert to a time series
```{r,echo = TRUE}
Gregorovitch = xts(Gregorovitch, order.by = Gregorovitch$V1)
Olivander = xts(Olivander, order.by = Olivander$V1)
```

##d) Create a dygraph
```{r,echo = TRUE}
#merge together
wands = cbind(Gregorovitch, Olivander)
names(wands)[2] = "Gregorovitch_wands"
names(wands)[4] = "Olivander_wands"

#dygraph
#install.packages("dygraphs")
library(dygraphs)

dygraph(wands, main = "Wands Sold Over Time", xlab = "Year", ylab = "Number of Wands")  %>% 
  dySeries("Olivander_wands", label = "Olivander")  %>% 
  dySeries("Gregorovitch_wands", label = "Gregorovitch")  %>% 
  dyOptions(colors = RColorBrewer::brewer.pal(5, "Set1"))  %>% 
  dyShading(from = "1995-1-1", to = "1999-1-1", color = "skyblue")  %>% 
  dyHighlight(highlightSeriesOpts = list(strokeWidth = 2))  %>% 
  dyRangeSelector(height = 80)
```